I’m writing to apply for the remote Android Developer position at your Milan office. I graduated with Bachelor of Software Engineering from NUST, Pakistan in 2018 and am currently enrolled in Master of Computer Science at TU Kaiserslautern, from where I expect to graduate in September 2022. I am passionate about programming and have been developing native Android apps since 2015, which is why I am applying for this position.

Over the past few years, I have developed a large number of Android apps, both as my side projects and working for other clients as a freelancer. I am proficient in both Java and Kotlin languages, and familiar with latest Android development tools. I constantly keep my knowledge about Android tools and Kotlin language itself by reading documentations and watching tutorials. Through my Software Engineering degree, I also know about good software architecture and design patterns, and I know how to write maintainable, testable and scalable code. I am also familiar with the use of Git for version control. Most of the source code I have written is available on GitHub (\url{https://github.com/saifkhichi96}), and I have also used GitLab in the past. I have experience with CI using GitHub Actions and Travis CI, and I know how to write good documentation for my code. I would also like to draw your attention towards my portfolio website \url{https://www.saifkhichi.com/projects/} where details of all my past projects are shared, and I explain my Android development work in detail.

I believe that I am a flexible person who learns fast and is able to solve problems efficiently, whether on my own or in teams. I understand that communication is key to teamwork, and I can speak English language fluently. I am a non-EU citizen with a temporary German resident permit for students at the moment, and I am mainly interested in working at your Milan office. However, for that I would need an Italian work permit and relocation support from you. I can start working from October 2022. Thank you for your consideration and time. I look forward to hearing back from you soon.